### 2021-07-03 docs/manuscript/manuscript.tex
Discuss PCA results

\subsection*{Change in morphogenetic field size}
We wanted to evaluate if the GRNs evolved in our model with a morphogenetic
field size of 30 cells could produce the desired pattern in morphogenetic fields
with a different number of cells. For this reason, we calculated the fitness of
each GRN in morphogenetic fields with 10, 20, 40, and 50 cells. In these
simulations we redefined the morphogen gradient in such a way that the initial
and final concentration were constant in all the fields (\nameref{S5_Fig}).
In order to know if topologies with the same topology had a similar fitness
in the different fields, we performed a Principal Component Analysis in
Scikit-learn~0.24.2~\cite{sklearn} using the fitness values of each GRN in
the four different fields.

@@

Robustness is an important feature of patterning mediated by morphogens, and
the GRNs involved can be selected in an evolutionary process not only by its final
steady state but also by its ability to buffer noise~\cite{lo_robust_2015, exelby_2021}.
In our study, the most abundant topologies were
found to be part of highly connected clusters in the neutral network, and this fact
indicates that these topologies are both robust to quantitative changes in the
strength of interactions and diffusion and degradation parameters as well as to
qualitative changes in the topology itself. As robustness and evolvability are
not mutually exclusive properties~\cite{wagner_robustness_2008}, it is likely
that these topologies are also evolvable.

>>>>

\subsection*{Change in morphogenetic field size}
We wanted to evaluate if the GRNs evolved in our model with a morphogenetic
field size of 30 cells could produce the desired pattern in morphogenetic fields
with a different number of cells. For this reason, we calculated the fitness of
each GRN in morphogenetic fields with 10, 20, 40, and 50 cells. In these
simulations we redefined the morphogen gradient in such a way that the initial
and final concentration were constant in all the fields (\nameref{S5_Fig}A).
In order to know if topologies with the same topology had a similar fitness
in the different fields, we performed a Principal Component Analysis in
Scikit-learn~0.24.2~\cite{sklearn} using the fitness values of each GRN in
the four different fields.

@@

Robustness is an important feature of patterning mediated by morphogens, and
the GRNs involved can be selected in an evolutionary process not only by their final
steady state but also by their ability to buffer noise~\cite{lo_robust_2015, exelby_2021}.
In our study, the most abundant topologies were
found to be part of highly connected clusters in the neutral network, and this fact
indicates that these topologies are both robust to quantitative changes in the
strength of interactions and diffusion and degradation parameters as well as to
qualitative changes in the topology itself. As robustness and evolvability are
not mutually exclusive properties~\cite{wagner_robustness_2008}, it is likely
that these topologies are also evolvable.\\

In contrast to this robustness to
qualitative and quantitative changes, we found that many GRNs were susceptible
to changes in morphogenetic field size, but interestingly, GRNs with the same
topology behave in different ways for each field size (\nameref{S5_Fig}C),
indicating that the specific values of network parameters are more important
than the network topology when it comes to producing the same pattern at
different scales.
